\centerline{\emph{\LARGE{Acknowledgments }}}

\vspace*{1cm}
\emph{
\lettrine[lines=2]{I}\\t is with great respect and profound gratitude that I extend my heartfelt thanks to all those who, directly or indirectly, contributed to the successful completion of this project. Your support, presence, encouragement, and invaluable guidance have been instrumental to our achievement, making this journey both enriching and unforgettable.
\newline \newline \indent First and foremost, I would like to express my sincere appreciation to Mr. Taoufik Ladhari, my academic supervisor, and Mr. Fawzi Msahli, my co-supervisor. The privilege of being guided by their expertise throughout this project has been invaluable. Their unwavering support, insightful feedback, and constant encouragement were instrumental to my progress, shaping not only this work but also my understanding of the field.
\newline \newline \indent I am equally grateful to Mr. Saddem Ben Salah, my industrial supervisor, for welcoming me to XPERT-MECA and offering me the opportunity to carry out my internship in such a dynamic and professional environment. His technical guidance, mentorship, and trust significantly enriched my practical knowledge and deepened my understanding of the industrial world. 
\newline \newline \indent Also, I want to convey my utmost respect and gratitude to the esteemed members of the jury for the honor they have bestowed upon me by examining and evaluating this modest contribution. I hope that this work meets their esteemed standards and expectations. \\
\newline  \newline \indent Finally I dedicate this work to my beloved parents, whose boundless love, countless sacrifices, and unwavering support have been the very foundation of my journey and success.This achievement is not mine alone; it belongs to you both. It is a reflection of your sacrifices, your dreams for me, and the endless support you have given without asking for anything in return.}
